Denotational Semantics of General Payment Primitives, and Its Payment System

### 2022-10-03 packages/spec-haskell/yellowpaper/Paper1.tex
alright, abstract done, will do a proof reading before sending out

\begin{abstract}
    \begin{center}
        (Some distant lyrics as the placeholder for the actual abstract)

        Money, money, money

        Must be funny

        In the rich man's world

        Money, money, money

        Always sunny

        In the rich man's world

        \

        Ah, all the things I could do

        If I had a little money

        It's a rich man's world

        It's a rich man's world
    \end{center}
\end{abstract}

@@

\subsection{$\mathcal{M}$ - Category of Money Distribution}

>>>>

\begin{abstract}
Payment systems in information age are still largely modeled after their analog predecessors. While
some electronic money payment systems do utilize computing technology and Internet, this paper
presents a case that a true modernization can still be done by (a) making payments happening
continuously over time (b) involving more than two parties in a payment if necessary (c) having
compositional financial contracts.

This paper first explores the foundation of modern payment system, which consists of a money
distribution model, payment primitives, payment execution systems of financial contracts and
different forms of money mediums. Then the paper uses \textit{denotational semantics} to formally
define payment primitives for modern payment system. Lastly, this paper also includes an overview
of \textit{Superfluid protocol}, a reference implementation of the payment primitives and a its
payment system.

This paper also includes literate Haskell code that compiles as the constructive artifact for the
formal specifications.

\end{abstract}

@@

\subsection{$\mathcal{M}$ - Syntax for Money Distribution}
